THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-09-06 DishReflectometry/Paper1_v3.tex
Corrected references section 2

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spectrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
The redshifted 21 cm spatial power spectrum is defined as
\begin{equation}
  P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
\label{eq:delay-power-spectrum}
\end{equation}
where
\begin{equation}
  k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{equation}
The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
$f_{21}$:rest frame frequency of the 21~cm radiation.\\
$f$: observation frequency.\\
$z$: cosmological redshift corresponding to the frequency of observation.\\
 $\Delta B$: bandwidth centered at the observation frequency.\\
 $k_\textrm{B}$: Boltzmann constant.\\
 $D\equiv D(z)$ comoving distance along the line of sight\\
 $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
\indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec. \ref{sec:multiple}. In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{\textbf{Antenna Reception With Multiple Reflections}}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

>>>>

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spectrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
The redshifted 21 cm spatial power spectrum is defined as
\begin{equation}
  P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
\label{eq4}
\end{equation}
where
\begin{equation}
  k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
 \label{eq5}
\end{equation}
The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
$f_{21}$:rest frame frequency of the 21~cm radiation.\\
$f$: observation frequency.\\
$z$: cosmological redshift corresponding to the frequency of observation.\\
 $\Delta B$: bandwidth centered at the observation frequency.\\
 $k_\textrm{B}$: Boltzmann constant.\\
 $D\equiv D(z)$ comoving distance along the line of sight\\
 $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
\indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed.
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{\textbf{Antenna Reception With Multiple Reflections}}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}
